\Huge Visualization Interactivity Perception Research \\ on Data Journalism

### 2017-05-01 paper/main.tex

% \documentclass{proc}
% \documentclass[journal, letterpaper]{IEEEtran}
\documentclass[9pt,journal,compsoc]{IEEEtran}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{framed}
\usepackage{ragged2e}
\usepackage[listings,skins]{tcolorbox}
\usepackage[skipbelow=\topskip,skipabove=\topskip]{mdframed}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{caption}
\linespread{1}
\usepackage{float}
\setlength{\parskip}{0.4em}
\usepackage{subcaption}

@@

 Through this practical experiment, we dedicate to explore the relationship between user perception and interactive, two hypothesis are proposed:
 1. Higher level of interactive visualization can improve user's perception for data journalism
 2. Higher level of interactive visualization can reduce the misleading by article.

@@

\section{Experiment}
\large
\begin{table}
	\centering
		\begin{tabular}{|c|c|c|c|}
		\hline
     	&Level 0&Level 1&Level 2\\
     	\hline
            		&Static diagram&Drag & Level 2 plus\\ 
        Interactive& with tool tips&Multiple Charts&instruction，\\
					&             &   			&Sort Buttons\\
     	\hline
        \end{tabular}
     \caption{Three level of Interactive}
\end{table}
\subsection{Interection Levels Design}
In this experiment we design three levels of interactive visualization as indicated in table 1. To control the noise, all of the three levels of interactive visualization are embeded in an news website.\\
\textbf{Level 0:} Designed with zero interaction. The website contains the original article, and static U.S. map, scatter plot, with tool tips that demonstrate the given data. \\
\textbf{Level 1:} Designed with some interaction such as drag, mouse over effect, hover multiple charts. \\
\textbf{Level 2:} Finally, for this design, the bi-directional visual interaction pattern is used. Buttons to sort attributes are also introduced. These interactions are implemented based on U.S. map and scatter plot.

@@

\section{Evaluation}
\large
\subsection{Data Preprocessing}
The Fig.3 shows the the box plot of time spend for each question. We can see that there are some extreme low values at the button. When we scan through the corresponding answers we found that the accuracy and skip rate are also lower than expect. Based on such fact, we assuming that people spend 5 seconds less on each question is not taking the test seriously. In the following evaluation, we exclude the responses that spend less than 5 seconds on average for each question to make our analysis more convincing.
\begin{figure} [H]
  \centering
  \includegraphics[width=0.32\textwidth]{TimeSpendBox.PNG}
  \caption{Time Spend for Each Question}
  \label{fig:6}
\end{figure}
\subsection{Time Spend Evaluation}
Fig.4(a) show the average time spend for three levels in each question. From the bar chart we can see that in general, users tend to spend less on Level 1 than Level 0. However, when it comes to the high interactivity(Level2), the results shows that the users might spend more time on answering questions.
\subsection{Accuracy and Skip Rate Evaluation}
\textbf{Accuracy Rate.} Fig.4(b) shows the average accuracy rate for three levels in each question. For Question 1-4(Map Visualizations), each levels results shows somewhat random, but combined with the skip rate, we can gain some insight from them. For question 5, surprisingly, the higher interactive level doesn't helps users to get higher correctness.

@@

\section{Discussion}
\large
\subsection{Test Result Analysis}

\subsection{Limitations and Future Research}
We took a step out to evaluate if the different level of interactive can affect the audience of the news papers online in data journalism. For the experiment itself, we used five kinds of common interactive method in the experiment, as the front-end technology fast changing, the future research should consider not only the classic methods but the latest visualization technology. Meanwhile, with the time limit, we can not find more random sample to join this experiment, it should be improved in the future work.

@@

\bibitem{c13} Web Interactivity Perception Experiment on Real articles L0: https://yiminlin1994.github.io/gradfinal/index1.html
\bibitem{c14} Web Interactivity Perception Experiment on Real articles L1: https://yiminlin1994.github.io/gradfinal/index2.html
\bibitem{c15} Web Interactivity Perception Experiment on Real articles L2: https://yiminlin1994.github.io/gradfinal/index3.html 
\bibitem{c13} 
\bibitem{c13}

>>>>

% \documentclass{proc}
% \documentclass[journal, letterpaper]{IEEEtran}
\documentclass[9pt,journal,compsoc]{IEEEtran}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{framed}
\usepackage{ragged2e}
\usepackage[listings,skins]{tcolorbox}
\usepackage[skipbelow=\topskip,skipabove=\topskip]{mdframed}
\usepackage{pbox}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{caption}
\linespread{1.1}
\usepackage{float}
\setlength{\parskip}{0.4em}
\usepackage{subcaption}

@@

 Through this practical experiment, we dedicate to explore the relationship between user perception and interactive, four hypotheses are proposed in our study, which are listed in Section 3.

@@

\section{Experiment}
\large
\begin{table}
	\centering
		\begin{tabular}{|c|c|c|c|}
		\hline
     	&Level 0&Level 1&Level 2\\
     	\hline
            		&Static diagram&Drag & Level 2 plus\\ 
        Interactive& with tool tips&Multiple Charts&instruction，\\
					&             &   			&Sort Buttons\\
     	\hline
        \end{tabular}
     \caption{Three level of Interactive}
\end{table}
\subsection{Hypotheses}
Based on the related work, we decide to divide the interactivity perception experiment into three levels. The hypothesis we put forward are listed as follows.

\textbf{Hypothesis 1.} Users are easier to perceive the information with higher interaction.\\
\textbf{Hypothesis 2.} Users are more willing to engage in the story with higher interaction.\\
\textbf{Hypothesis 3.} Higher level of interactive visualization can improve user's perception for data journalism.\\
\textbf{Hypothesis 4.} Higher level of interactive visualization can reduce the misleading by article.\\

\subsection{Interection Levels Design}
In this experiment we design three levels of interactive visualization as indicated in table 1. To control the noise, all of the three levels of interactive visualization are embeded in an news website.\\
\textbf{Level 0:} Designed with zero interaction. The website contains the original article, and static U.S. map, scatter plot, with tool tips that demonstrate the given data. \\
\textbf{Level 1:} Designed with some interaction such as drag, mouse over effect, hover multiple charts. \\
\textbf{Level 2:} Finally, for this design, the bi-directional visual interaction pattern is used. Buttons to sort attributes are also introduced. These interactions are implemented based on U.S. map and scatter plot.

@@

\section{Evaluation}
\large
\subsection{Data Preprocessing}
The Fig.3 shows the the box plot of time spend for each question. We can see that there are some extreme low values at the button. When we scan through the corresponding answers we found that the accuracy and skip rate are also lower than expect. Based on such fact, we assuming that people spend 5 seconds less on each question is not taking the test seriously. In the following evaluation, we exclude the responses that spend less than 5 seconds on average for each question to make our analysis more convincing.
\begin{figure} [H]
  \centering
  \includegraphics[width=0.32\textwidth]{TimeSpendBox.PNG}
  \caption{Time Spend for Each Question}
  \label{fig:6}
\end{figure}
\subsection{Time Spend Evaluation}
Fig.4(a) shows the average time spend for three levels in each question. From the bar chart we can see that in general, users tend to spend less on Level 1 than Level 0. However, when it comes to the high interactivity(Level2), the results shows that the users might spend more time on answering questions.
\subsection{Accuracy and Skip Rate Evaluation}
\textbf{Accuracy Rate.} Fig.4(b) shows the average accuracy rate for three levels in each question. For Question 1-4(Map Visualizations), the average accuracy rate of each level shows somewhat random, but combined with the skip rate, we can gain some insight from them. For Question 5-6 (Scatter Plot Visualization), the average accuracy are expected to

@@

\begin{figure} [H]
  \centering
  \includegraphics[width=0.32\textwidth]{MisleadingQ6.png}
  \caption{Fig 5. The comparison between the "Misleading Answer" and "Right Answer".}
  \label{fig:6}
\end{figure}

\section{Discussion}
\large
\subsection{Test Result Findings}
This part will discuss the test result in details and conclude the insights from the test result.

For Question 1-4, time spend for Level 1 is less than Level 0, while time spend for Level 3 is more than the other two. So we can conclude that Some interactivity could help users to recognize the data faster. However, if the interactivity is too complex, users might have trouble the use the interaction. Therefore, designers must measure the complexity of their interactivity. The accuracy rate is random, so we can conclude that designed unsuitable interactivity can cause a misleading effect. However, since the Level 0 shows a significant higher skip rate in Question 1-4, we can conclude that the rich interactivity would make a users engage more in the test. The low skip rate of Level 1 and Level 2 indicates that a rich interactivity would make users more willing to participate in the test and feel more confident on the test.

\subsection{Limitations and Future Research}

We took a step out to evaluate if the different level of interactive can affect the audience of the news papers online in data journalism. For the experiment itself, we used five kinds of common interactive method in the experiment, as the front-end technology fast changing, the future research should consider not only the classic methods but the latest visualization technology. Meanwhile, with the time limit, we can not find more random sample to join this experiment, it should be improved in the future work.

@@

\bibitem{c13} Web Interactivity Perception Experiment on Real articles L0: https://yiminlin1994.github.io/gradfinal/index1.html
\bibitem{c14} Web Interactivity Perception Experiment on Real articles L1: https://yiminlin1994.github.io/gradfinal/index2.html
\bibitem{c15} Web Interactivity Perception Experiment on Real articles L2: https://yiminlin1994.github.io/gradfinal/index3.html
